In thesis we constructed many new and more efficient Non-Interactive Zero-Knowledge proofs. In general, we showed that any set of quadratic equations of the type $b(b-1)=0$ and any set of linear equations with variables in $\Z_q$ have a proof whose size is linear in the number of variables and independent of the number of equations. In the case equations where variables are group elements, we showed that any set of linear equations have a proof whose size is linear in the number of variables and independent of the number of equations, with the drawback that the CRS must be fixed to the specific set of equations. We then moved to the case of higher degree equations, which can be equivalently seen as Set-Membership proofs --a proof of membership in the set of roots of the equation in the case where the variables are $\Z_q$ elements-- and has the advantage that can also be applied to the case where the variables are group elements (since it is not clear how to define higher degree equations where variables are group elements). We showed that any set of Set-Membership proof have a proof whose size is linear in the size of the set and linear the number of variables, but independent of the number of proofs. When the set is a subset of $\Z_q$ or the CRS is fixed to a specific subset of $\GG_s$, we showed that the proof is logarithmic in the size of the set and linear in the number of variables, but independent of the number of proofs.

In Chapter \ref{sec:agg-asym} we constructed more efficient proofs for sets of linear equations over $\Z_q$ and $\GG_s$. Our results extends the result of Jutla and Roy \cite{C:JutRoy14} from one-sided to two-sided equations. We also showed that the same techniques allows to build QA-NIZK constant size proofs of membership in linear subspaces of $\GG_1\times\GG_s$, which extends the constant size QA-NIZK of membership in linear subspaces of $\GG_s$ from \cite{EC:LPJY14,C:JutRoy14,EC:KilWee15,EC:AbdBenPoi15}. Finally we showed how to extend the Linearly Homomorphic Structure-Preserving Signatures of Libert et al. \cite{EC:LPJY14} from the message space $\GG_s^n$ to $\GG_1^m\times\GG_2^n$.

In Chapter \ref{sec:bits} we constructed a constant-size QA-NIZK proof that a set of commitments open to a bit-string or equivalently, we showed that a set of equations of the type $b(b-1)=0$ have a proof of size linear in the number of variables and independent of the number of equations. In the first part of the chapter we devoted to case where the commitment is perfectly binding and then showed that it allowed more efficient ring signatures and threshold Groth-Sahai proofs. In the second part we devoted to case where the commitment is computationally binding and length-reducing. We introduced an extension of Pedersen commitments and showed that for this commitments we can build a QA-NIZK proof that there exists an opening in $\bits^n$.

In Chapter \ref{sec:shuf-rp} we constructed QA-NIZK proofs that many commitments open to elements in a set, where the proof size is linear in the size of the set and independent of the number of commitments. We then showed how to use this this primitive to construct more efficient proofs of correctness of a shuffle and range proof under standard assumptions.

In Chapter \ref{sec:extras} we showed how to construct a more efficient ring signature and also showed that the results from Chapter \ref{sec:shuf-rp} can be improved to logarithmic size proofs.

\section{Open Problems}

\subsubsection{Aggregation of any Groth-Sahai Proof}
One of the main problems that remains open is to extend (or give an impossibility result) the efficiency improvements to any kind of equation, that is, construct proofs for a set of pairing product equations of size linear in the number of variables and independent of the number of equations. One indication that this could be impossible is the fact that shrinking group to group commitments do not exists \cite{EC:AbeHarOhk12} and that in our results for quadratic equations over $\Z_q$ we used in a crucial way the Multi-Pedersen commitments (which are shrinking commitments). A related or more simple question is whether linear equations over $\GG_s$ allow more efficient proofs without computing an ad-hoc CRS. We note that this case suffer the same problem, since for example the values 
$$\left\{\pmatri{{[a_{1,1}]_1}\\\vdots\\{[a_{1,k}]_1}},\ldots,\pmatri{{[a_{n,1}]_1}\\\vdots\\{[a_{n,k}]_1}}\right\}$$
included in the CRS can be thought as commitment keys of a length reducing commitment scheme (much like Multi-Pedersen commitments). The fact that the discrete logarithms of the equation's constants appears multiplied by this commitment keys is to allow to compute a length reducing commitment of the constants of the equation.

The impossibility result of Abe et al. is proven when the key generation and commitment functions are \emph{algebraic}, that is, the group elements are only ``manipulated'' using the group operations and its actual representation is ignored.
A possible avenue to bypass this impossibility is to take in count the actual representation of group elements. For example, we can commit to the binary representation of a group element using Multi-Pedersen commitments. The problem now is that the commitment is not homomorphic and it is not straightforward to use use with Groth-Sahai proofs. However, it should be still theoretically possible if we rely on general results for NP-complete languages, as done in Sect. \ref{sec:log-ring-signature}.
Indeed, the NP-completeness of quadratic equations over $\Z_q$ allows to translate any set of pairing product equations to a set of quadratic equations over $\Z_q$. For example to translate an equation $e([x]_1,[y]_2)=[0]_T$, we can consider the circuit which computes the function $C_e:\bits^{\ell_1}\times \bits^{\ell_2} \to\bits^{\ell_T}$, where $\ell_s$ is the size of the representation of an element of $\GG_s$, and express the circuit as a set of quadratic equations.

\subsubsection{More efficient proofs of quadratic equations}
Mostly all of our constructions derived from the proofs that many commitments open to a bit-string suffer from the same drawback: the CRS is quadratic in the size of the bit-string, which of course limits their applicability. In Sect. \ref{sec:bits-extensions} we showed that when the bit-string is of weight 1 the CRS can be made linear, however this is not always the case and the problem is still open.
%Bootle et al. \cite{EC:BCCGP16} construct a proof system which, although in a different setting, would help to shed lights on how to solve this problem. There, at some of the protocol, it is computed a set of elements which can be arranged matrix such that the $i,j$ th is the coefficient of the monomial $x^{i-j}$. Thereby, all elements at positions $i,j$ such that $i-j=k$ are coefficients of the same monomial $x^k$. Despite this very informal description, we can apply this idea as follows: compute commitments keys $[\vecb{g}_i],[\vecb{h}_j]_2$ in such a way that $\vecb{g}_i\vecb{h}_j=\vecb{g}_{k+i} \vecb{h+k}^\top$ .
 
\subsubsection{Theoretical $\Theta(\log n)$ Shuffles}
It is interesting to explore if similar techniques to those from Sect. \ref{sec:log-ring-signature} allow to construct a $\Theta(\log n)$ proof of correctness of a shuffle. The improved aZKSMP should allow to almost prove that a set of ciphertexts are a correct shuffle. We say almost, because the aZKSMP only allows to show that each output-plaintext is in the set of input-plaintexts and thus there might be repeated elements. The challenge is then to show that the aZKSMP do not contain repeated indices.

\subsubsection{Extend results for high-degree equations to circuits}
Gentry and Wichs showed that any sublinear NIZK proof must rely on Non-Falsifiable assumptions if the language is ``hard'' (say an NP-hard language) \cite{STOC:GenWic11}. This result seems to rule out any sublinear NIZK proof if the assumption is any ``DDH-like'' assumption. However, many cryptographically interesting languages are seem not to be NP-hard. For example, the language of vectors in a subspace of $\GG_1$ seems not be NP-hard and has constant size proofs. In fact, what we believe that is happening is that the language is in fact ``easy'' given the appropriate trapdoor (in this case a basis of the kernel of the generating matrix) while an NP-hard language should not have such a trapdoor.

In general, in many languages the statement is the commitment to some value and we want to prove some assertion about the opening. Given a circuit $C$ and a commitment key $ck$, we define the following language
$$
\Lang_{ck,C}:= \{([\vecb{c}_1]_1,\ldots,[\vecb{c}_n]_1,a)\in\GG_1^2\times\bits^k:= \exists [x_i]_1\in\GG_1,w_i\in\Z_q \text{ s.t. } [\vecb{c}_i]_1=\GS.\Com_{ck}([x_i]_1;w_i)\text{ and }C([x]_1,a)=1\}.
$$
Many interesting problems can be instantiated in this way: in Ring Signatures $[x]_1$ is the verification key, $a$ the description of the ring, and $C$ outputs 1 iff $[x]_1$ is in the ring; b) in a shuffle $[\vecb{c}_1]_1,\ldots,[\vecb{c}_n]_1$, $n=2m$, are cyphertexts and $C([x]_1,\ldots,[x_n]_1)=1$ iff the first $m$ openings are a permutation of the las $m$ openings; c) in Groth-Sahai proofs the openings are the variables and the $C$ outputs 1 iff the variables satisfies the equations. In fact, the only interesting problem which is not of this type is a Range Proofs and is an interesting questions if there are other problems not of this type.

Using techniques from \cite{EC:GroOstSah06} one can construct NZIK proofs for $\Lang_{ck,C}$ of size $\Theta(|C|)=\Theta(n+|a|)$, since $|C|\leq n+|a|$, which boils down to compute linear Shuffles or Ring Signatures. We have seen on Sect. \ref{sec:log-ring-signature} that there exists ring signatures of size $\Theta(\log n)$, combining our results for aZKSMP and the same ``reduction to circuit'' approach. We beleive that this is an indication that more efficient proofs for languages $\Lang_{ck,C}$ exists.


