In this chapter we describe a more efficient ring signature and an improved aggregated set-membership proof.

Our ring signature is the first of size $\Theta(\sqrt[3]{n})$ without random oracles. We highlight that this is the first asymptotic improvement since Chandran et al.'s ring signature \cite{ICALP:ChaGroSah07}. To prove security we make use of the \emph{Permutation Pairing assumption}, introduced by Groth and Lu \cite{AC:GroLu07}, which is defined on symmetric groups (or type I). Although it might be possible to find a natural asymmetric counterpart of the assumption, we choose the simple solution and construct our ring signature on symmetric groups. We note that this is the only construction on symmetric groups given in this work.

In the second part of this section we construct a QA-NIZK proof system for the language
\[
\Lang_{ck,\mathsf{set}}^n:=\left\{\begin{array}{l}
([\grkb{\zeta}_1]_1,\ldots,[\grkb{\zeta}_n]_1,S):\exists w_1,\ldots,w_n\in\Z_q \text{ s.t. } S\subset\Z_q\\
\text{ and } \forall i\in [n]\ [\grkb{\zeta}_i]_1=\GS.\Com_{ck}(x_i;w_i)\wedge x_i\in S
\end{array}\right\},
\]
with proof size $\Theta(\log n)$. In Section~\ref{sec:improved-aZKSMP-group-case} we show how to extend these ideas to show membership in the language
\[
\Lang_{ck,S}^n:=\left\{\begin{array}{l}
([\grkb{\zeta}_1]_1,\ldots,[\grkb{\zeta}_n]_1):\exists w_1,\ldots,w_n\in\Z_q \text{ s.t. } S\subset\GG_1 \\
\text{ and } \forall i\in [n]\ [\grkb{\zeta}_i]_1=\GS.\Com_{ck}([x_i]_1;w_i)\wedge [x_i]_1\in S
\end{array}\right\},
\]
with proof size $\Theta(\log n)$, for any \(S\subset\GG_1\).

The first case is the more general form of a set-membership proof where the set is dynamically chosen. In the second case each instance of the proof system is fixed to a specific set (encoded in the CRS) and is the same notion of the proofs for ``fixed sets'' from Section \ref{sec:bits-applications}. We note that the aggregated set-membership proofs for $S\subset\GG_s$ from Chapter \ref{sec:shuf-rp} are proofs of membership in $\Lang_{ck,S}^n$.

There is a straightforward application of the improved aZKSMP. In the proof of a Shuffle from Section \ref{sec:shuffle}, the size of the proof that $[\matr{F}]\in\Lang_{ck,S}^n$ can be reduced from $2n+\Theta(1)$ to $\Theta(\log n)$ and thus the total proof size is reduced from $4n+o(n)$ to $2n+o(n)$.

In Section \ref{sec:opt-rs} we consider another application of the improved aZKSMP: theoretical $\Theta(\log n)$ ring signatures without random oracles. Although the constants hidden in the asymptotic size of the proof are only polynomially bounded on the security parameter, we interpret this construction as a feasibility result for $\Theta(\log n)$ ring signatures (note that only $\Theta(\sqrt{n})$ ring signatures where known up to this work).


